A comparison of approaches to Kazakh to Kyrgyz machine translation

### 2015-02-19 2015-eamt-kazkir/2015-eamt-kazkir.tex
harg
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59026 72bbbca6-d526-0410-a7d9-f06f51895060
stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59027 72bbbca6-d526-0410-a7d9-f06f51895060

Besides these systems, several previous works on making machine translation systems between Turkic languages 
exist, although to our knowledge none are publicly available except for the Turkish--Azerbaijani pair available through Google Translate.\footnote{\url{http://translate.google.com}}
Some MT systems have been reported that translate between Turkish and other Turkic languages, 
including Turkish--Crimean Tatar \citep{altintas01},
Turkish--Azerbaijani \citep{hamzaoglu93}, Turkish--Tatar \citep{suleymanov08}, and
Turkish--Turkmen \citep{tantug07}, though none of these have been released to a public audience.

@@

>>>>

Besides these systems, several previous works on making machine translation systems between Turkic languages 
exist, although to our knowledge none are publicly available except for the Turkic--Turkic pairs (including Azerbaijani, Kazakh, Turkish, and Uzbek) available through Google Translate.\footnote{\url{http://translate.google.com}}
Some MT systems have been reported that translate between Turkish and other Turkic languages, 
including Turkish--Crimean Tatar \citep{altintas01},
Turkish--Azerbaijani \citep{hamzaoglu93}, Turkish--Tatar \citep{suleymanov08}, and
Turkish--Turkmen \citep{tantug07}, though none of these have been released to a public audience.

@@

\begin{table}
  \begin{tabular}{|l|r|r|r|}
    \hline
    \textbf{System} & \textbf{PER} & \textbf{WER} & \textbf{BLEU} \\ 
    \hline
    RBMT            &              &              &               \\
    PBSMT            &              &              &               \\
    CBMT            &              &              &               \\
    \hline  
  \end{tabular}
\end{table}
